---
title: "Montréal Urban Perceptions Meeting"
date: January 26, 2023
format: 
  html:
    embed-resources: true
---

### Background

We want to explore how people's perceptions of urban trees varies with their sociodemographics. Specifically, we want to dig deeper into understanding people's perceptions in *Montréal*. We want to use the survey data to ask more pointed and meaningful questions about Montréal specifically (e.g., examine the issue of language).

There is potential for 2+ papers here. Following the first meeting, we decided that the questions of governance and management could be tackled by Emile in a separate paper, as he has a lot of expertise in this field.

This paper will be focused on questions regarding the valuation and beliefs surrounding urban trees (as opposed to questions of governance, tree knowledge, etc.)

------------------------------------------------------------------------

### Proposed Research Question

How are Montréal residents' values and beliefs concerning urban trees influenced by city type, country of origin, preferred language, dwelling type, education level?

-   **Dependent variables:**

    -   Tree Value survey questions (15) - e.g., How important to you are each of the following things about these trees: large old trees?
    -   Tree Beliefs (Negative) survey questions (12) - e.g., How much do you agree that the trees in your city or neighbourhood are ugly?    
    -   Tree Beliefs (Positive) survey questions (12) - e.g., How much do you agree that the trees in your city or neighbourhood are calming?

-   **Independent variables:**

    -   City type (inner, middle, outer, regional)
    -   Country of origin (Canadian born with Canadian born parents, Canadian born with parents born abroad, born abroad)
    -   Preferred language(English, French, Other with preferred official language English, Other with preferred official language French)
    -   Dwelling type (house, apartment in a house, apartment in a building, other, prefer not to answer)
    -   Education level (prefer not to answer, did not complete high school, high school, trade school, bac, masters, doc)
    
    
**Justification:** selected the variables that came out as important in street tree cover from Pham et al., 2017 + city type

**Hypothesis:** values and beliefs regarding trees are influenced by sociodemographics, as well as exposure to trees (street tree cover)

------------------------------------------------------------------------

### Street Tree Cover

**Discussion Question:** should we add street tree cover to our models?

-   Without adding street tree cover, we can measure the *total effect* of sociodemographics on people's values/beliefs (this includes the unmeasured effect of the influence of street tree cover on their values/beliefs)

```{dot}
//| fig-width: 8
//| fig-align: center
digraph G {
    
    bgcolor="transparent"
    node [style=filled,color=white]
    edge [color="black"]
    
    rankdir=LR
    
    Sociodemographics [shape=box]
    Tree_Values_Beliefs [shape=box]
    
    Sociodemographics -> Street_Tree_Cover;
    Sociodemographics -> Tree_Values_Beliefs;
    Street_Tree_Cover -> Tree_Values_Beliefs;
    
}
```

------------------------------------------------------------------------

### The Data

**Tree Values**

```{r, echo = F, eval = T, message=F, warning=F}
library(targets)
library(ggpubr)
library(tidyr)

mtl_clean <- tar_read(mtl_clean)

long <- pivot_longer(mtl_clean, cols = starts_with("uf_vals"))

ggboxplot(long, "name", "value", add = "jitter")
```

**Tree Beliefs (Negative)**

```{r, echo = F, eval = T, message=F, warning=F}
long <- pivot_longer(mtl_clean, cols = starts_with("beliefs_negatives"))

ggboxplot(long, "name", "value", add = "jitter")
```

**Tree Beliefs(Positive)**

```{r, echo = F, eval = T, message=F, warning=F}
long <- pivot_longer(mtl_clean, cols = starts_with("beliefs_positives"))

ggboxplot(long, "name", "value", add = "jitter")
```

**Explanatories**
