---
title: "Montréal Urban Perceptions Meeting"
date: January 26, 2023
format: 
  html:
    embed-resources: true
---

### Proposed Research Question

How are Montréal residents' values and beliefs concerning trees influenced by their culture (Canadian born), preferred language, dwelling type, education level, and city type?

**Justification:** selected the variables that came out as important in street tree cover from Pham et al., 2017 + city type

**Hypothesis:** values and beliefs regarding trees are influenced by sociodemographics, as well as exposure to trees (street tree cover)

------------------------------------------------------------------------

### Street Tree Cover

**Discussion Question:** should we add street tree cover to our models?

-   Without adding street tree cover, we can measure the *total effect* of sociodemographics on people's values/beliefs (this includes the unmeasured effect of the influence of street tree cover on their values/beliefs)

```{dot}
//| fig-width: 8
//| fig-align: center
digraph G {
    
    bgcolor="transparent"
    node [style=filled,color=white]
    edge [color="black"]
    
    rankdir=LR
    
    Sociodemographics [shape=box]
    Tree_Values_Beliefs [shape=box]
    
    Sociodemographics -> Street_Tree_Cover;
    Sociodemographics -> Tree_Values_Beliefs;
    Street_Tree_Cover -> Tree_Values_Beliefs;
    
}
```

------------------------------------------------------------------------

### The Data

**Tree Values**

```{r, echo = F, eval = T, message=F, warning=F}
library(targets)
library(ggpubr)
library(tidyr)

mtl_clean <- tar_read(mtl_clean)

long <- pivot_longer(mtl_clean, cols = starts_with("uf_vals"))

ggboxplot(long, "name", "value", add = "jitter")
```

**Tree Beliefs (Negative)**
```{r, echo = F, eval = T, message=F, warning=F}
library(targets)
library(ggpubr)
library(tidyr)

long <- pivot_longer(mtl_clean, cols = starts_with("beliefs_negatives"))

ggboxplot(long, "name", "value", add = "jitter")
```

**Tree Beliefs(Positive)**

```{r, echo = F, eval = T, message=F, warning=F}
library(targets)
library(ggpubr)
library(tidyr)

long <- pivot_longer(mtl_clean, cols = starts_with("beliefs_positives"))

ggboxplot(long, "name", "value", add = "jitter")
```

**Explanatories**
